### 2020-06-17 manuscript/internship_report.Rmd
add appendices

bibliography      : "report.bib"

@@

```{r calculate integrated complete likelihood criterion, include=FALSE}

# Compute ICL

ICL <- function(mod) {

  -2*logLik(mod, method = "classification") + npar(mod)*log(nobs(mod))

A2017.icl <- lapply(A2017.fit, function(stim) {
  out <- lapply(stim, function(subj) {
    out <- lapply(1:length(subj), function(mod) {

        icl <- try(-2*subj[[mod]][["LL"]] + 6*log(subj[[mod]][["N"]]))

        icl <- try(ICL(subj[[mod]]$model))

      return(ifelse(is.numeric(icl), icl, NA))
    })

# Create ICL weight plots

icl.plot <- lapply(A2017.icl, function(x) {

  p <- ggplot(data.long, aes(x = model, y = subject)) + geom_tile(aes(fill = weight)) +
    scale_x_discrete(name = "Number of states", labels = as.character(1:5)) +
    scale_y_discrete(name = "Subject") +
    scale_fill_distiller(name = "ICL weight", breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1), palette = "Spectral")

@@

# Appendix
# Technical Appendix
# References

>>>>

bibliography      : "report.bib"
appendix          : 
 - "report_appendix.Rmd"
 - "report_technical_appendix.Rmd"

@@

@@

# References
